k-Space Domain Parallel Transmit Pulse Design

### 2020-09-10 Manuscript/Conclusion.tex
wag added preamble
Wag all done, need to move to wiley template

\section*{Discussion and Conclusions}

A computationally efficient and highly parallelizable k-space domain pTx pulse design method was proposed.
The method adapts the k-space domain formulism proposed by Katscher et al \cite{katscher2003transmit}, which does not require the computationally expensive iterative processes in the conventional spatial domain design methods. The method advances the work of Katscher et al \cite{katscher2003transmit} by finely parallelizing the process of finding the system matrix. Furthermore, a technique inspired by a rapid GRAPPA calibration method \cite{luo2019grappa} is also included to further speed up the computation of each instance. The proposed k-space domain design method was evaluated through simulation upon an inner volume pulse design problem for MR Corticography, which can in turn enable submillimeter whole-cortex and cortex-specific imaging. The optimal parallelization parameters: thread number, patch width, and inclusion width, were found for this design problem. The proposed method reduced the computation time by 97\% compared to the conventional spatial domain design method, while producing equal inner volume suppression performance. And the abilities of the proposed method to accommodate k-space undersampling and correct off-resonance were also demonstrated to be equal to conventional spatial domain design method.

>>>>

%!TEX root = kPtx_paper.tex
\section*{Discussion}
\subsection*{Summary}
A small-tip-angle k-space domain parallel transmit pulse design algorithm was proposed
that divides up the calculation of a matrix relating a target excitation pattern to the pulses that produce it 
into a set of independent problems for patches of target excitation k-space locations,
each of which is influenced by a local neighborhood of points on the excitation k-space trajectory.
The division of the problem into patches of target locations creates an opportunity for fine parallelization,
while the limited neighborhood sizes lead to small problem sizes for each patch. 
Compared to the original k-space-based algorithm of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830},
the L-curve and matrix size results showed that 
the new algorithm produces much smaller matrix sizes that can be calculated more quickly,
with the tradeoff of increased excitation error or RF power. 
Results showed that the algorithm also enables compensation of off-resonance 
which has not previously been described in a k-space domain design. 
Compared to widely-used spatial domain method of Ref. \cite{Grissom:2006:MRM},
the new algorithm is non-iterative and can be finely parallelized to achieve shorter design times, 
and results showed that it can use coarser target grid sizes while avoiding Gibbs ringing, 
again with the tradeoff of increased excitation error or RF power.
The performance of off-resonance-compensated spatial domain and k-space domain pulse designs was similar,
and the methods were similarly sensitive to excitation k-space undersampling.

\subsection*{Applications and Extensions}
This work was initially motivated by the observation that spatial domain parallel pulse designs can be very slow
for 3D problems with large grid sizes, 
requiring both many iterations and considerable computation per iteration. 
It is anticipated that the proposed k-space domain algorithm will be most useful for these types of large $>$2D problems,
which include 3D spatial designs \cite{malik2012tailored} and 2D and 3D spatial-spectral designs \cite{stenger2000three,yang2010four,davids2016fast}
where full matrix construction and inversion is infeasible due to the problem size,
and an iterative design can require several minutes to solve. 
Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
This means that it could have a considerable computational speed advantage for magnitude least-squares designs \cite{setsompop2008magnitude,malik:mrm:2015}. 
The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost; 
Finally, while simple Tikhonov RF power regularization was used in the designs presented here,
more sophisticated regularization could be incorporated to, e.g., control peak RF power via adaptive regularization,
or to enforce array compression by projecting the weights into the null space of a compression matrix .
In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices
so they need not be re-computed as the regularization changes over iterations.

### 2020-09-10 Manuscript/kPtx_paper.tex
WAG done with Methods
Wag all done, need to move to wiley template

\documentclass[11pt]{article}
% Command line: pdflatex -shell-escape compulse.tex
\usepackage{geometry} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{times}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage[outerbars]{changebar}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage{verbatim}

@@

\section*{\underline{Abstract}} 
{\bf Purpose:}
To improve the computational efficiency of parallel transmission pulse design. 
\\[1em]
{\bf Methods:}
something
\\[1em]
{\bf Results:}
something
\\[1em]
{\bf Conclusion:}
something
\\[1em]
{\bf \noindent Key words:} Parallel Transmission; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation.

>>>>

\documentclass[11pt]{article}
% Command line: pdflatex -shell-escape compulse.tex
\usepackage{geometry} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{times}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage[outerbars]{changebar}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage{verbatim}
\usepackage{textcomp}

@@

\section*{\underline{Abstract}} 
{\bf Purpose:}
To accelerate the design of multidimensional parallel transmission pulses. 
\\[1em]
{\bf Methods:}
A k-space domain parallel transmission pulse design algorithm was proposed that
produces a sparse matrix relating a target excitation pattern to the pulses that produce it,
and can be finely parallelized. 
The algorithm was applied in simulations to the design of 3D SPINS pulses for inner volume excitation in the brain at 7 Tesla.
It was characterized in terms of the dependence of computation time, excitation error, and required memory
on algorithm parameters,
and it was compared to the spatial domain pulse design method in terms computation time, excitation error,
Gibbs ringing, and ability to compensate off-resonance.
\\[1em]
{\bf Results:}
The proposed algorithm achieved approximately 90\% faster pulse design compared to 
an iterative spatial domain method, with the same number of parallel threads,
with the tradeoff of increased excitation error and RMS RF amplitude. 
It reduced the memory required to store the design matrix by 98\% compared to a full matrix solution.
Even with a coarse design grid, the algorithm produced patterns that were free of Gibbs ringing.
It was similarly sensitive to k-space undersampling as the spatial domain method,
and was similarly capable of compensating for off-resonance.
\\[1em]
{\bf Conclusion:}
The proposed k-space domain algorithm accelerates and finely parallelizes parallel transmission pulse design,
with a modest tradeoff of excitation error and RMS RF amplitude.
\\[1em]
{\bf \noindent Key words:} Parallel Transmission; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation.
